%------------------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------------------

\cvsection{Experience}

%------------------------------------------------------------------------------
%	SECTION CONTENT
%------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------------------------------------

\cventry
{Postdoctoral Fellow}
{Massachusetts Institute of Technology}
{Cambridge, Massachusetts}
{Jun. 2017 - Exp. Jun. 2019}
{
\begin{cvitems}
\item {Transitioned data analysis method from conventional Excel-like
    spreadsheet to Python Scripting for improved automation and result
    reproducibility.}
\item {Increased the accuracy of experimental results by introducing new
    algorithm and data modeling method to our previous analysis techniques.}
\item {Built a remote pressure monitor web app for lab instruments to increase
    lab safety and productivity.}
\item {Created a custom jupyter notebook docker image that contains all the
    necessary packages for lab data analysis. Simplified environment setup for
    colleagues who are new to python.}
\end{cvitems}
}

%- ----------------------------------------------------------------------------

\cventry
{Research Assistant}
{University of Utah}
{Salt Lake City, Utah}
{Aug. 2011 - May. 2017}
{
\begin{cvitems}
\item {Designed, fabricated and maintained a sophisticated surface science
    apparatus from the ground up, as a result of a collaboration with 7 other
    research institutes.}
\item {Created multiple data analysis templates for processing lab data
    generated from the custom instrument.}
\item {Wrote LabView programs for data acquisition and system control.}
\item {Preliminary results disagreed with those documented by our collaborator.
    As a result, designed and conducted additional experiments, and upon data
    interpretation and literature search, discovered nanoparticle size effect.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\end{cventries}