%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Author:
% Yang Dai (daiy@mit.edu)
%
% Document Type:
% Cover Letter 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[11pt, letterpaper]{awesome-cv}

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm}
 
\fontdir[fonts/]

% Color for highlights
\colorlet{awesome}{awesome-red}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\begin{document}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

\name{Yang}{Dai}
\address{247 Presidents Lane, Quincy, Massachusetts, 02169, US}
\mobile{(+1) 510-363-6334}

\email{daiy@mit.edu}
\homepage{www.yangdai.info}
\github{superyang713}
\linkedin{yangdai713}

\position{
  Data Science{\enskip\cdotp\enskip}Programming{\enskip\cdotp\enskip}Engineering}

\makecvfooter{\today}{}{\thepage}

%-------------------------------------------------------------------------------
% RECIPIENT/POSITION/LETTER INFORMATION
%-------------------------------------------------------------------------------

\recipient{Hiring  Team}{Zero Gravity Labs.\\70 Richmond Street, Suite 201\\
  Toronto, ON M5C 1N8, CA}

\letterdate{\today}

\lettertitle{Job Application for Data Scientist}

\letteropening{Dear Michael Cohen,}

\letterclosing{Sincerely,} 


%-------------------------------------------------------------------------------

\makecvheader

\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------

\begin{cvletter}

%-------------------------------------------------------------------------------

\lettersection{About Me}

I would like to introduce myself as an applicant for the Data Scientist
position at Zero Gravity Labs. I am confident in my ability to perform as a data
scientist at Zero Gravity Labs due to my extensive education and research experience.
%------------------------------------------------

\lettersection{Why Zero Gravity Labs?}

AI is undoubtly the next big thing and Zero Gravity Labs is actively
experimenting new ideas and bring them to fruition. Experimentation and
innovation are my key driving forces in my scientific research. I truly
appreciate those companies who are willing to take risks experimenting new
ideas, and aim to make a difference in the world.

%------------------------------------------------

\lettersection{Why Me?}
Throughout my research history, I have been designing countless experiments in
order to prove my theory. I even designed and built various sophisticated
equipments for the purpose of my research, so I am no stranger of
experimentation and innovation.

In my current research role at MIT, I use Python extensively (Numpy, Pandas,
Sci-kit Learn). I might be a physical chemist, but I am a fast and active
learner. I have a deep understanding of machine learning algorithms, and have
used various machine learning frameworks. I also develop many interests in the
field of programming, such as web development, cloud computing, and big data,
but I know these are just tools to get things done. I constantly try out new
tools, some of which are for my work, but mostly are just for my pure curiosity.
There was once a project proposal that required me to develop a web app
to monitor our research equipment condition in real time. It was a short project
(1 weeks), so I had to rapidly learn and apply multiple new skills within days,
such as Django, JavaScript, and AWS. I am therefore very confident that I could
quickly ramp up and add value to your team - both in Python-based work; and any
other languages/tools/algorithm you use.

I believe that programming is the closest thing to magic, and I never stop
thinking what I can do with it. When I come up with a new idea, I take actions
and try my best to turn it into reality. I now want to apply this
passion in my everyday work - especially in a team like yours that values
intellectual excellence and innovation.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing

\end{document}