%------------------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------------------

\cvsection{Experience}

%------------------------------------------------------------------------------
%	SECTION CONTENT
%------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------------------------------------

\cventry
{Postdoctoral Fellow}
{Massachusetts Institute of Technology}
{Cambridge, Massachusetts}
{Jun. 2017 - Exp. Jun. 2019}
{
\begin{cvitems}
\item {Currently using various surface characterization techniques, such as Mass
    Spectrometry, Auger Electron Spectroscopy, and Electron Energy Loss
    Spectroscopy, to explore whether modification of the Nickel electronic
    structure by formation of a surface alloy with Au will result in
    un-activated dissociative adsorption of molecular hydrogen.}
\item {Transitioned data analysis method from conventional Excel-like
    spreadsheet to Python Scripting for improved automation and result
    reproducibility.}
\item {Increased the accuracy of experimental results by introducing new
    algorithm and data modeling method to our previous analysis techniques.}
\end{cvitems}
}

%- ----------------------------------------------------------------------------

\cventry
{Research Assistant}
{University of Utah}
{Salt Lake City, Utah}
{Aug. 2011 - May. 2017}
{
\begin{cvitems}
\item {Designed and fabricated a sophisticated cluster deposition apparatus with
    the capability of depositing mass-selected noble metal clusters. The mass
    selection was accomplished by a custom built quadrupole mass filter. Click
    \href{https://www.yangdai.info/portfolio/beam-source-for-size-selected-metal-clusters}{here}
    for more information.
  }
\item {Upgraded an old VG ESCALAB MKII surface science instrument with
    functioning XPS, QMS, and sputter gun. Added metal evaporators for
    growing alumina and Tin thin film, a sample stage for ALD, and a sample
    heating/cooling stage on the manipulator to conduct TPD in front of a
    differentially pumped mass spectrometer.}
\item {Wrote LabView programs for data acquisition and system control.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\end{cventries}