%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Author:
% Yang Dai (daiy@mit.edu)
%
% Document Type:
% Cover Letter 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[11pt, letterpaper]{awesome-cv}

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm}
 
\fontdir[fonts/]

% Color for highlights
\colorlet{awesome}{awesome-red}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\begin{document}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

\name{Yang}{Dai}
\address{247 Presidents Lane, Quincy, Massachusetts, 02169, US}
\mobile{(+1) 510-363-6334}

\email{daiy@mit.edu}
\homepage{www.yangdai.info}
\github{superyang713}
\linkedin{yangdai713}

\position{
  Data Science{\enskip\cdotp\enskip}Programming{\enskip\cdotp\enskip}Research}

\makecvfooter{\today}{}{\thepage}

%-------------------------------------------------------------------------------
% RECIPIENT/POSITION/LETTER INFORMATION
%-------------------------------------------------------------------------------

\recipient{Hiring  Team}{Scotiabank\\44 King Street West\\Toronto, ON M5H 1H1}

\letterdate{\today}

\lettertitle{Job Application for Data Scientist}

\letteropening{Dear Hiring Team,}

\letterclosing{Sincerely,} 


%-------------------------------------------------------------------------------

\makecvheader

\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------

\begin{cvletter}

%-------------------------------------------------------------------------------

\lettersection{About Me}

I would like to introduce myself as an applicant for the Data Scientist position
at Scotiabank, a prestigious and reputable name in innovative finance
techonology. I am confident in my ability to perform as a Data Scientist at
Scotiabank due to my extensive education and research experience.

%------------------------------------------------

\lettersection{Why Scotiabank?}

Scotiabank is in the great transition shifting its focus from the volumn of data
collected to the actual use of this information to support business
imperatives. Data science is the key to achieve this. And as a data scientist, I
want to be part of this transition and prove my value.

%------------------------------------------------

\lettersection{Why Me?}
In my current research role at MIT, I use Python extensively (Numpy, Pandas, Sci-kit
Learn), but there was once a project proposal that required me to develop a web
app to monitor our research equipment condition in real time. It was a short
project (2 weeks), so I had to rapidly learn and apply new multiple skills
within days, such as Django, JavaScript, HTML, Nginx, and AWS. I am therefore
very confident that I could quickly ramp up and add value to your team - both in
Python-based work; and any other languages/tools you use.

I have been part of many team-based projects during my research. I played a key
role in a research project that involved 7 other research institues. I was
repsonsible for making nanoparticle samples for collaborators, and through clear
communication, I was able to supply samples that met their expectations.

I have actively pursued numerous data science courses and attended seminars at
MIT to build my knowledge base; and frequently applied techniques I have learned
to my work. I have channeled this passion into a personal blog as well. I now
want to apply this passion in my everyday work - especially in a team like yours
that values intellectual excellence.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing

\end{document}