%------------------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------------------

\cvsection{Experience}

%------------------------------------------------------------------------------
%	SECTION CONTENT
%------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------------------------------------

\cventry
{Postdoctoral Fellow}
{Massachusetts Institute of Technology}
{Cambridge, Massachusetts}
{Jun. 2017 - Exp. Jun. 2019}
{
\begin{cvitems}
\item {Studied interaction between molecular hydrogen and modified Nickel/Gold
    surface alloy with numeric and analytical tools.}
\item {Explained and matched experimental observations to theoretical models
    using fitted statistical simulations and analytic solutions.}
\item {Transitioned data analysis method from conventional Excel-like
    spreadsheet to Python and SQL database with popular scientific and ML libraries,
    such as Numpy, Pandas, Keras, and PySpark for improved automation and result
    reproducibility.}
\item {Daily use of Linux Shell and Python scripts for data processing and analysis.}
\item {Automated simple work tasks with programming, such as creating a custom
    docker image for consistent working envrionment across the whole research group, and
    building an online status monitor for lab instruments.}
\item {Presented research results to general as well as expert audiences
    through seminars, conferences, talks, and posters.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\cventry
{Research Assistant}
{University of Utah}
{Salt Lake City, Utah}
{Aug. 2011 - May. 2017}
{
\begin{cvitems}
\item {Made major contribution to the development of in-house software, which is used
    for data acquisition and system control.}
\item {Created data analysis libraries in Python for processing and analyzing
    large datasets generated from a surface science instrument.}
\item {Developed a novel techinique to extract information from spectroscopic
    data that lead to uncovering unknown nanoparticle size effect.}
\item {Designed and fabricated a sophisticated surface science apparatus from
    the ground up, as a result of a collaboration with 7 other research institutes.}
\end{cvitems}
}

%------------------------------------------------------------------------------

\end{cventries}