%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Author:
% Yang Dai (daiy@mit.edu)
%
% Document Type:
% Cover Letter 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[11pt, letterpaper]{awesome-cv}

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm}
 
\fontdir[fonts/]

% Color for highlights
\colorlet{awesome}{awesome-red}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\begin{document}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------

\name{Yang}{Dai}
\address{247 Presidents Lane, Quincy, Massachusetts, 02169, US}
\mobile{(+1) 510-363-6334}

\email{daiy@mit.edu}
\homepage{www.yangdai.info}
\github{superyang713}
\linkedin{yangdai713}

\position{
  Data Science{\enskip\cdotp\enskip}Programming{\enskip\cdotp\enskip}Engineering}

\makecvfooter{\today}{}{\thepage}

%-------------------------------------------------------------------------------
% RECIPIENT/POSITION/LETTER INFORMATION
%-------------------------------------------------------------------------------

\recipient{Hiring  Team}{EMAGIN Clean Technologies Inc.\\151 Charles Street West\\Kitchener, ON N2G 1H6}

\letterdate{\today}

\lettertitle{Job Application for Data Scientist}

\letteropening{Dear Holly Warwick,}

\letterclosing{Sincerely,} 


%-------------------------------------------------------------------------------

\makecvheader

\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------

\begin{cvletter}

%-------------------------------------------------------------------------------

\lettersection{About Me}

I would like to introduce myself as an applicant for the Data Scientist position
at EMAGIN, an innovative technology company that combines AI with engineering. I
am confident in my ability to perform as a Data Scientist at EMAGIN due to my
extensive education and research experience.

%------------------------------------------------

\lettersection{Why EMAGIN?}

AI is undoubtly the next big thing and EMAGIN is actively meshing data science
with process engineering. And as a physical chemist with the background of both
engineering and data science, EMAGIN is definitely one of the few companies that
can appreciate my true value.

%------------------------------------------------

\lettersection{Why Me?}
In my current research role at MIT, I use Python extensively (Numpy, Pandas, Sci-kit
Learn), but there was once a project proposal that required me to develop a web
app to monitor our research equipment condition in real time. It was a short
project (2 weeks), so I had to rapidly learn and apply new multiple skills
within days, such as Django, JavaScript, HTML, Nginx, and AWS. I am therefore
very confident that I could quickly ramp up and add value to your team - both in
Python-based work; and any other languages/tools you use.

I have been part of many team-based projects during my research. I played a key
role in a research project that involved 7 other research institues. I was
repsonsible for making nanoparticle samples for collaborators, and through clear
communication, I was able to supply samples that met their expectations.

I have actively pursued numerous data science courses and attended seminars at
MIT to build my knowledge base; and frequently applied techniques I have learned
to my work. I have channeled this passion into a personal blog as well. I now
want to apply this passion in my everyday work - especially in a team like yours
that values intellectual excellence.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing

\end{document}